---
title: "normal_scores"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{normal_scores}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4
)
```

```{r setup}
library(quantiles)
```

It is not hard to see `Normality` assumption in many Statistical context. One of the ways to check the normality is Quantile-Quantile plot, shortly Q-Q plot.

To draw the plot, we need `Normal Score` theoretical quantiles of the data, and `Standard Score`, sample quantiles.

Function `normal_scores` helps us to calculate these.

For example, in normally distributed case

```{r}
set.seed(1)
dat_norm<-rnorm(30)
with(normal_scores(dat_norm),
     plot(x = normal_score, y = standard_score))
```

On the other hand, in non-normally distributed case

```{r}
set.seed(1)
dat_exp<-rexp(30,2)
with(normal_scores(dat_exp),
     plot(x = normal_score, y = standard_score))
```

